Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-03 doc/PRF2022/Supplementary.tex
updated Supplementary.tex

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 0.5 that are initially confined in a square box.
 The simulation results show the relaxation with the use of all three boundary condition

%form a self-enclosed bilayer structure. The simulation result shows the vesicle relaxation and the fluid pressure inside the JP vesicle decreases to 0 after a period of time.
%The color field from blue to red shows the magnitude of fluid pressure and the range from 0 to 0.1. All dark blue dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
%This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
%We adopt the relaxed configuration and place the JP vesicle in the shear flow. The simulation result shows a tank-treading motion when the shear rate is $\chi=0.005$.
%The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
%This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S3. Structures in a Shear Flow with Ruptures} 
%Using the same setup demonstrated in Movie S2, we show the simulation result for 
%inter-monolayer slip by tracking a pair of particles (blue and yellow). After $t=4000$, 
%the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
%This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S4. Structures in a Taylor-Green Flow without Ruptures} 
%The numerical results show that the JP vesicle starts to have rupture phase at the shear rate $\chi=0.0655$. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion. This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
%There are two relaxed JP vesicles suspended in a shear flow. The two centroids are at coordinates $(-25,0)$ and $(25,0)$ in nm. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion. This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\

>>>>

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 0.5 that are initially confined in a square box.
The simulation results show the relaxation with the use of all three boundary conditions.
The color on the boundary from blue to red shows the magnitude of the boundary data and 
the range is from $\min g(\xx)$ to $\max g(\xx)$. All final configurations are adopted in 
simulations with hydrodynamic flows. The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow. 
In this movie, there is no apparent structural rupture in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
$\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
In this movie, there is no apparent structural rupture in each case. For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the bilayer, 
$V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow. 
In this movie, some clear structural ruptures occur in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the bilayer, 
$\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma = 0.15$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.
In order to observe the structure behaviors at later time, we stabilize the frame by tracking the center of mass position of all JP. \\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
In this movie, some clear structural ruptures occur in each case. For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
$V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.\\
